%!TEX root = ../dissertation.tex
\chapter{Conclusion}
\label{cap:conclusion}

\newthought{In conclusion}, the implementation of an application for managing smart-locks and Airbnb rentals has been shown to be a valuable addition to the current self check-in workflow. The application can provide a convenient and secure way for Airbnb hosts to manage access to their properties while also improving the overall guest experience. The use of the smart-lock technology ensures that access is granted only to authorized individuals and also eliminates the need for key exchanges, which can be time-consuming and potentially unsafe. Furthermore, the ability of hosts to remotely monitor and manage access to their properties through the application provides added peace of mind. Overall, the implementation of this application has been found to be a successful and practical solution for managing smart-lock and Airbnb rentals. Additionally, integration with Airbnb allows for easy management of multiple properties and bookings.
\\ One of the most significant benefits of this technology is the convenience it provides for both hosts and guests. With the ability to remotely control access to the property, hosts no longer have to worry about coordinating key exchanges and can instead focus on managing their properties and bookings. Guests also benefit from the convenience of being able to access their rental at any time, without the need to coordinate key pick-up or drop-off.

Another important benefit is the added security layer provided by using a smart-lock. With the ability to remotely monitor access to the property, hosts can ensure that only authorized guests can enter. This added security also provides peace of mind for guests, knowing that their rental is protected and secure.

Integration with Airbnb also allows for easy management of multiple properties and bookings. Hosts can now manage all their listings and reservations from one central location, saving them time and effort. In addition, guests can easily book and access multiple properties through the same platform, providing a seamless and convenient experience.

Overall, the implementation of an application managing smart-lock and Airbnb has the potential to greatly benefit the vacation rental industry. It provides added convenience, security, and revenue for hosts, while also improving the customer experience for guests. It is clear that this technology should be considered for future developments in the vacation rental industry and could potentially become the new standard for managing vacation rentals.

Eventually, the technologies used in this project shows how it is possible to implement a robust and secure application. There are, of course, few compromises between usability and security, which are widely justified. The requirements outlined in the analysis bring to light the limitation and the strong points. The design of the software is an advanced example of what technology can do nowadays with less effort in implementation, in order to dedicate more time to the actual analysis.